Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 conclusion.tex
yes

\gordon{I think that except for the DevOps slogan, this is redundant and
too dense.  I would replace the first three paragraphs with something
like this:} We designed a prototype environment for exploration, sharing,
presentation, and publishing. The exploration part didn't work out so well,
but people like sharing stuff and integrating web and analysis languages.

@@

We deployed RCloud in a community of working data scientists.
Experience with the RCloud prototype provides evidence that data
science teams and the organizations in which they work benefit from
having capabilities that support collaboration and integrate
the entire visual analytics process. Specifically, features for
sharing and publishing were eagerly adopted. Features for data
single-user data exploration, that compete with existing mature
tools, were not accepted as readily. Some experienced users
fashioned their own workflow so they could keep using familiar EDA tools.

The study has provided a step toward practical ``DevOps for data science''
and reproducible, publishable experiments.  Possible next steps are
to incorporate richer recommendation techniques, to provide fine-grained
information security, and to improve the usability of the human interface.

>>>>

%\gordon{I think that except for the DevOps slogan, this is redundant and too dense.  I would replace the first three paragraphs with something like this:} We designed a prototype environment for exploration, sharing, presentation, and publishing. The exploration part didn't work out so well, but people like sharing stuff and integrating web and analysis languages.

@@

We deployed RCloud in a community of working data scientists.
Experience with the prototype provides evidence that data
science teams and the organizations in which they work benefit from
having capabilities to support collaboration and to integrate
the entire visual analytics process. We found that features for
sharing and publishing were eagerly adopted. Features for 
single-user data exploration, that compete with existing mature
tools, were not accepted as readily. Some experienced users
fashioned their own workflow so they could keep using familiar EDA tools.

This study has provided a step toward practical ``DevOps for data science''
and reproducible, publishable experiments.  Possible next steps are
to incorporate richer recommendation techniques, to provide fine-grained
information security, and to improve the usability of the human interface.
